Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-12 paper.tex
Use high solidity in conclusion

In this study it was demonstrated that the performance of a cross-flow turbine
becomes essentially $Re$-independent at a Reynolds number based on turbine
diameter of $Re_D \approx 10^6$, or an approximate Reynolds number based on
blade chord of $Re_c \approx 2 \times 10^5$.

\todo[inline]{Should we discuss that these results depend on turbine type, and
solidity? Lower solidity turbines may only achieve a "linear" regime, not a
truly Re-indept regime. Additional issues such as blade termination/strength of
tip vortices?}

>>>>

In this study it was demonstrated that the performance of a high solidity
($c/R=0.28$) cross-flow turbine becomes essentially $Re$-independent at a
Reynolds number based on turbine diameter of $Re_D \approx 10^6$, or an
approximate Reynolds number based on blade chord of $Re_c \approx 2 \times
10^5$.

\todo[inline]{Issues such as blade termination/strength of tip vortices?}
